\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{enumitem}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}
\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% CV Starts frm here

\begin{document}

% Heading
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Thamilmaran Mohanarasa}} & Email: \href{mailto:thamilmaranm@proton.me}{thamilmaranm@proton.me}\\
  \href{https://github.com/Maranmaxi2022}{Github: ~~Maranmaxi2022} & Mobile: +94-77-3028-673 \\
\end{tabular*}

% About me
\section*{About me}
\vspace{-8pt}
Software developer passionate about building web-based systems and applied ML/AI.

% Education
\section*{Education}
\vspace{-8pt}
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l r}
  \textbf{University of Moratuwa} & {Colombo, Sri Lanka} \\
  {BScHons in Information Technology} & {June 2021 -- August 2025} \\
\end{tabular*}

\vspace{0.5em} % space between entries

\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l r}
  \textbf{Kn/ Kilinochchi Central College} & {Kilinochchi, Sri Lanka} \\
  {G.C.E Advanced Level, Physical Science Stream (A, 2B)} & {Aug 2019} \\
\end{tabular*}

% Experience
\section*{Experience}
\vspace{-8pt}
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l r}
  \textbf{\href{https://qnetwork.ai/}{QNetwork}} & {Remote} \\
  {AI Engineer - Intern} & {Apr 2024 - Sep 2024} \\
\end{tabular*}
\vspace{-6pt}

\begin{itemize}\itemsep -2pt
  \item Built a predictive model for Canadian house prices using a dataset focused on Canadian properties.
  \item Using Python-based libraries such as NumPy, Pandas, and TensorFlow to analyze data and develop models.
  \item Developed an API to retrieve crime data for specific regions in Ontario, Canada.
  \item Created dynamic front-end interfaces using React and implemented Bootstrap CSS for responsive design.
  \item Conducted manual testing to ensure software quality and performance.
\end{itemize}

% Skill Summary
\section*{Skills}
\vspace{-8pt}
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} p{5cm} p{13cm} @{}}
\textbf{Programming Languages:}   & Python, Java, JavaScript \\
\textbf{Packages:}  & Pandas, NumPy, Matplotlib, Sklearn, TensorFlow, PyTorch\\
\textbf{Web Development:}   & HTML, CSS, React, Spring Boot \\
\textbf{Technologies:}       & Git, Docker, Excel, Postman \\
\end{tabular*}

% Projects
\section*{Projects}
\vspace{-8pt}
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l r}
  \textbf{\href{https://github.com/Maranmaxi2022/FYP}{Multi-Modal Popularity Forecasting with a Time-Series Transformer}} & {Final Year Research} \\
\end{tabular*}
\vspace{-12pt}
\begin{itemize}\itemsep -2pt
  \item Replaced the LSTM head in the SMTPD baseline with a Time-Series Transformer (TST) while keeping the original multi-modal encoders (ResNet-101 thumbnail, mBERT text, categorical \& numeric features) and the same Composite Gradient Loss.
  \item Implemented principled handling of Early Popularity (EP): treat Day-1 as input and shift prediction targets to Days 2-30 to avoid leakage; added windowed evaluation (Day-7/14/30 and 1-30 or 2-30 ranges).
  \item\textbf{Results:}
  \begin{itemize}\itemsep -2pt
  \item \textbf{Component study:} AMAE $\downarrow$ 0.746 $\rightarrow$ 0.723 and ASRC $\uparrow$ 0.958 $\rightarrow$ 0.960 with TST vs. LSTM.
  \item \textbf{Horizon MAE (lower is better):} 0.710 (Day-7), 0.737 (Day-14), 0.745 (Day-30) with competitive rank correlation.
  \item \textbf{EP effect:} Including Day-1 (EP) as input reduces error by $\sim$50\%+ vs. w/o - EP while maintaining strong late-day performance.
  \end{itemize}
  \item\textbf{Tech:} PyTorch, Transformers (mBERT), ResNet - 101, TST, 5 - fold evaluation, Spearman/MAE metrics, reproducible training \& eval scripts.
\end{itemize}

\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l r}
  \textbf{\href{https://github.com/Maranmaxi2022/Pet-Finder}{PetFinder Pawpularity - Image Only Regression}} & {July 2025 - Aug 2025} \\
\end{tabular*}
\vspace{-12pt}
\begin{itemize}\itemsep -2pt
  \item Designed a two-part pipeline: (1) pretrained image embeddings → SVR stacks, and (2) fine-tuned ViT models for regression.
  \item Implemented stratified K-Fold CV with OOF tracking; constrained weight search on OOF to blend SVR + ViT predictions.
  \item Added practical post-processing (prediction clipping; optional scaling) and deterministic runs (fixed seeds, shared folds).
  \item \textbf{Result:} $\sim$[17.1] RMSE OOF on $\sim$9.9k training images (↓$\sim$17\% vs naive baseline 20.6 RMSE)
  \item\textbf{Tech:} PyTorch, timm, RAPIDS cuML, scikit-learn, SciPy
\end{itemize}

\newpage
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l r}
  \textbf{\href{https://github.com/Maranmaxi2022/Top-Voice}{Top Voice - consultation \& booking platform}} & {Aug 2025 - Ongoing} \\
\end{tabular*}
\vspace{-12pt}
\begin{itemize}\itemsep -2pt
  \item Implemented creator profiles, availability calendars, time-slot booking, and end-to-end session flow.
  \item Designed REST APIs with validation, pagination, and structured error handling; secured with JWT + role-based access (admin/creator/user).
  \item Modeled MySQL schema (users, profiles, availability, bookings, sessions, reviews) with indexes for search \& conflict checks.
  \item\textbf{Tech:} React, Spring Boot, MySQL
\end{itemize}

% Referees
\section*{Referees}
\vspace{-8pt}
\begin{minipage}[t]{0.48\textwidth}
\textbf{Dr.\ (Ms.) Ahangama S,}\\
PhD (NUS), BSc (Hons) IT (Moratuwa),\\
Senior Lecturer (Grade I),\\
Faculty of Information Technology,\\
University of Moratuwa.
\end{minipage}\hfill
\begin{minipage}[t]{0.48\textwidth}
\textbf{Sanjeepan S.,}\\
ML Engineer - H2O.ai.\\
\end{minipage}

\end{document}